\textit{A young boy with a tree made of trees}: \\ Domain Adaptation of an LSTM-based Image Caption Generation Model

### 2023-01-04 paper/paper.tex
Splitting the writing

\subsection{The image captioning model}
\subsection{Flickr8k}
\subsection{imageCLEF}
\subsection{Human judgement questionnaire}

\section{Results}

Here we should summarize our results, in terms of:
\begin{enumerate}
    \item where did the performance exceed the best prior performance (we got BEST checkpoints?)
    \item which models actually generated reasonable captions? where did they start falling apart?
    \item subjectively, which captions were best? include the questionnaire results here or subsequently
\end{enumerate}
Include figures and tables as much as we can/as much as is reasonable.

\section{Discussion}

@@

\section{Conclusions and further work}

>>>>

\subsection{The image captioning model \textbf{DK}}
\subsection{Flickr8k \textbf{MS or DK}}
\subsection{imageCLEF \textbf{MS or DK}}
\subsection{Human judgement questionnaire \textbf{MS}}

\section{Results \textbf{MS and DK?}}

Here we should summarize our results, in terms of:
\begin{enumerate}
    \item where did the performance exceed the best prior performance (we got BEST checkpoints?) \textbf{DK}
    \item which models actually generated reasonable captions? where did they start falling apart? \textbf{MS or DK}
    \item subjectively, which captions were best? include the questionnaire results here or subsequently \textbf{MS}
\end{enumerate}
Include figures and tables as much as we can/as much as is reasonable.

\section{Discussion \textbf{MS and/or DK}}

@@

\section{Conclusions and further work \textbf{MS and/or DK}}
